\documentclass[11pt,letterpaper,sans]{moderncv}

\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.88]{geometry}
\usepackage{color}

\definecolor{lightgrey}{rgb}{0.6,0.6,0.6}
\definecolor{darkgrey}{rgb}{0.4,0.4,0.4}
\firstname{\textcolor{lightgrey}{Will}}
\familyname{\textcolor{darkgrey}{Fuqua}}
\title{Software Engineer}
\address{38844 Steeple Chase Apt 27104}{Farmington Hills, MI 48331}
\mobile{248-987-8787}
\email{wafuqua@gmail.com}
\homepage{fuqua.io}
\recomputelengths

\begin{document}

\maketitle
\vspace*{-5mm}

\section{Education}
\cventry{2005--2009}{BS, Software Engineering, Computer Science}{Rose-Hulman Institute of Technology}{}{}{GPA: 3.52/4.00, Magna Cum Laude}
\cvline{Minors}{Mathematics, Spanish Language}

\section{Skills}
\subsection{Proficient With}
\cvline{Languages}{C\#, Java, Python, JavaScript, HTML, CSS, SQL}
\cvline{Technologies}{.NET Stack (ASP.NET MVC, Web API, WCF), JEE Stack (Spring, JMS), SQL Server, NHibernate, Django, AJAX, REST API design, jQuery, Backbone.js, \LaTeX{}, Bash}
\cvline{Tools}{Linux, Visual Studio, Eclipse, Vim, Git, Subversion}
\subsection{Have Experience With}
\cvline{Languages}{Scala, F\#, Clojure, PHP, ColdFusion}
\cvline{Technologies}{Android, Silverlight, PostgreSQL, MySQL, CakePHP, Ogre3D, GTK, Qt}

\section{Experience}
\cventry{2009--Present}{Senior Consultant}{X by 2}{Farmington Hills, MI}{}{
    \begin{itemize}
        \item Claims System Integration
            \begin{itemize}
                \item Helped move an enterprise's insurance claim platform away from mainframe technologies to a modern service-oriented architecture.
                \item Responsible for design and implementation of an enterprise document managment system integration.
            \end{itemize}
        \item Electronic Medical Record System
            \begin{itemize}
                \item Developed the data model and web services for a care delivery platform that provides physicians with a single source for patient health information management.
            \end{itemize}
        \item Life Insurance Portal
            \begin{itemize}
                \item Created an insurance portal for members to view and manage accounts details.
                \item Worked with a team to design and implement a secure messaging platform for confidential customer communication.
                \item Created AJAX Google Maps pages to help customers locate nearby offices and activities.
            \end{itemize}
        \item Debt Counseling Education System
            \begin{itemize}
                \item Developed a portal that allows customers to take courses and examinations for bankruptcy certification.
                \item Created web services in order to integrate disparate technology platforms to create a seamless end-user experience.
            \end{itemize}
    \end{itemize}
}

\section{Activities}
\cventry{2009--Present}{Coffee House Coders}{}{}{}{}
\cventry{2009--Present}{Michigan!/usr/group}{Linux User Group}{}{}{Board Member for 2012, 2013}
\cventry{1998--2005}{Boy Scouts of America}{}{}{}{Eagle Scout}

\end{document}

